### 2019-06-25 2-Chapters/Conclusion/conclusion.tex
Lots of typos on Ch1 etc

Then we presented our Python library SMPyBandits \cite{SMPyBandits,SMPyBanditsJMLR}, by detailing
its purpose and qualities, its organization, and an overview of its usage.
%
Our library allows any researcher to easily implement numerical simulations of stochastic or piece-wise stochastic problems of single- or multi-players multi-armed bandits.
SMPyBandits is distributed on GitHub and Pypi freely, under an open-source license (MIT License), and it is extensively documented (at \href{https://SMPyBandits.GitHub.io}{\texttt{SMPyBandits.GitHub.io}}).
% Our library allows any researcher to easily run numerical simulations of different kinds of multi-armed bandit problems, requiring only a small knowledge of Python thanks to its documentation, its well-designed API, and many examples of simulation scripts and configuration files included.

@@

Another interesting direction of future work is to study non-stationary distributed multi-players bandits, to unify the models from Chapter~\ref{chapter:5} and~\ref{chapter:6}.
A natural extension of the non-stationary model is to consider non-communicating players cooperating in a decentralized way to play the same bandit game, as it was proposed recently in \cite{WeiSrivastava18Distributed}.
%
We could also build on the proof technique used in \cite{WeiSrivastava18Abruptly}, even if we are interested in removing the hypothesis that player $j$ knows its ID $j\in[M]$ before starting to play.
%
A promising direction is to directly try to join our contributions from Chapter~\ref{chapter:5} and~\ref{chapter:6}, and propose an efficient algorithm using three parts:
\klUCB{} indexes for arm selection,
\MCTopM{} for orthogonalization (\ie, dealing with collisions),
and the Bernoulli GLR break-point detector for non-stationarity (\ie, dealing with abrupt changes).
The three parts should be connected, the same way we built \GLRklUCB{} by connecting both components.
We propose the idea of incorporating the detected change-points by B-\GLR{} test in the orthogonalization procedure: after any change-point is detected, the player is not sitting anymore.
Analyzing this strategy is left as a future work.

>>>>

Then we presented our Python library SMPyBandits \cite{SMPyBanditsJMLR,SMPyBandits}, by detailing
its purpose and qualities, its organization, and an overview of its usage.
%
Our library allows any researcher to easily implement numerical simulations of stochastic or piece-wise stochastic problems of single- or multi-players multi-armed bandits.
SMPyBandits is distributed on GitHub and Pypi freely, under an open-source license (MIT License), and it is extensively documented (at \href{https://SMPyBandits.GitHub.io}{\texttt{SMPyBandits.GitHub.io}}).
% Our library allows any researcher to easily run numerical simulations of different kinds of multi-armed bandit problems, requiring only a small knowledge of Python thanks to its documentation, its well-designed API, and many examples of simulation scripts and configuration files included.

@@

Another interesting direction of future work is to study non-stationary distributed multi-players bandits, to unify the models from Chapter~\ref{chapter:5} and~\ref{chapter:6}.
A natural extension of the non-stationary model is to consider non-communicating players cooperating in a decentralized way to play the same bandit game, as it was proposed recently in \cite{WeiSrivastava18Distributed}.
%
We could also build on the proof technique used in \cite{WeiSrivastava18Abruptly}, even if we are interested in removing the hypothesis that player $j$ knows its ID $j\in[M]$ before starting to play.
%
A promising direction is to directly try to join our contributions from Chapter~\ref{chapter:5} and~\ref{chapter:6}, and propose an efficient algorithm using three parts:
\klUCB{} indexes for arm selection,
\MCTopM{} for orthogonalization (\ie, dealing with collisions),
and the Bernoulli GLR break-point detector for non-stationarity (\ie, dealing with abrupt changes).
The three parts should be connected, the same way we built \GLRklUCB{} by connecting both components.
We propose the idea of incorporating the detected change-points by B-\GLR{} test in the orthogonalization procedure \MCTopM: after any change-point is detected, the player is not sitting anymore.
Analyzing this strategy is left as a future work.

### 2019-06-25 3-Appendices/2-Appendix/appendix2.tex
Lots of typos on Ch1 etc

\paragraph{Motivations for anytime algorithms.}
%
As introduced in Chapter~\ref{chapter:2},
an online reinforcement learning algorithm is \emph{anytime} if it does not need to know in advance the horizon $T$ of the experiment.
%
Depending on the context of the practical application of interest, it might be unrealistic to assume to know in advance $T$. We give two examples to illustrate where this prior knowledge can be realistic or not.
On the one hand, consider clinical trials: it is likely that the number of patients is known before starting the trial, and for instance we refer to all the research that studies the setting of fixed-time best-arm identification \cite{audibert2010best,Garivier16BAI}.
On the second hand, consider cognitive radio and decentralized MAB learning implemented on IoT devices (like we present it in Chapter~\ref{chapter:4}): usually a learning step corresponds to an uplink and then downlink message sent and received by the IoT device, and so the time horizon $T$ denotes the total number of such messages. While it can be assumed that the device will run for instance for $10$ years (as it is advertised by some companies), many kinds of application such as medical sensors or connected fields cannot predict the number of total communications before setting up the device.

For this later range of applications, it is of highest interest to be able to use low-cost MAB algorithms that do not rely on prior knowledge of the problem for which they will be applied, and especially do not need to know the horizon $T$.
In this thesis,
while we proposed in Chapter~\ref{chapter:5} any-time algorithms solving the presented problem of stationary multi-players bandit, our solution for the problem of non-stationary MAB problem studied in Chapter~\ref{chapter:6} does rely on a prior knowledge of the horizon $T$.
It is interesting to know what is the best approach to fix this weakness: work more and design algorithms that are inherently any-time, or use a generic technique to avoid depending on a prior knowledge of $T$, and automatically transform our non-anytime approach to make it anytime.

\paragraph{Solution to ``patch'' a non-anytime algorithm.}
%
A well-known technique to obtain an anytime algorithm from any non-anytime algorithm is the ``Doubling Trick'', as first introduced in \cite{CesaLugosi06} and used for instance in \cite{Auer10,AuerGajaneOrtner18}.
%
In the context of adversarial or stochastic multi-armed bandits,
the performance of an algorithm is measured by its regret,
and we study two families of sequences of growing horizons (geometric and exponential)
to generalize previously known results that certain doubling tricks can be used to conserve certain regret bounds.
In a broad setting, we prove that a geometric doubling trick can be used to conserve (minimax) bounds in $R_T = \cO(\sqrt{T})$ but \emph{cannot} conserve (distribution-dependent) bounds in $R_T = \cO(\log T)$.
We give insights as to why exponential doubling tricks may be better, as they conserve bounds in $R_T = \cO(\log T)$, and are close to conserving bounds in $R_T = \cO(\sqrt{T})$.
Interestingly, we prove that they conserve bounds of the mixed form $R_T = \cO(T^{\gamma} (\log(T))^{\delta})$, for $0<\gamma<1$ and $\delta>0$, and so an exponential doubling trick could be used to obtain an anytime version of the algorithm we propose for non-stationary bandits, \GLRklUCB{} in Chapter~\ref{chapter:6}.
However, our study was only focussing on stationary bandit, and it is left as a future work to explore the harder case of piece-wise stationary problems.

@@

To conclude this work, we would need to complete the study of the doubling tricks, and instead of focussing on two families (geometric and exponential), we need to completely characterize the doubling tricks that allow to preserve certain regret bound.
Such doubling is given either by the function mapping the current time $t$ to the current estimate of the horizon $T(t)$, or the sequence $(T_i)_{i\in\N^*}$ of successive estimates of the horizons.
We are interested in pursuing this work, in the hope of finding an intermediate sequence, growing faster than a geometric but slower than an exponential doubling sequence, that can preserve both worlds, problem-dependent bounds in $\cO(\log(T))$ and problem-independent bounds in $\cO(\sqrt{T})$.

>>>>

\paragraph{Motivations for anytime algorithms.}
%
As introduced in Chapter~\ref{chapter:2},
an online reinforcement learning algorithm is \emph{anytime} if it does not need to know in advance the horizon $T$ of the experiment.
%
Depending on the context of the practical application of interest, it might be unrealistic to assume to know in advance $T$. We give two examples to illustrate where this prior knowledge can be realistic or not.
On the one hand, consider clinical trials: it is likely that the number of patients is known before starting the trial, and for this model we refer to all the research that studies the setting of fixed-time best-arm identification \cite{audibert2010best,Garivier16BAI}.
On the second hand, consider cognitive radio and decentralized MAB learning implemented on IoT devices (like we present it in Chapter~\ref{chapter:4}): usually a learning step corresponds to an uplink and then downlink message sent and received by the IoT device, and so the time horizon $T$ denotes the total number of such messages. While it can be assumed that the device will run for instance for $10$ years (as it is advertised by some companies \cite{Centenaro16}), many kinds of application such as medical sensors or connected fields cannot predict the number of total communications before setting up the device.

For this later range of applications, it is of highest interest to be able to use low-cost MAB algorithms that do not rely on prior knowledge of the problem for which they will be applied, and especially do not need to know the horizon $T$.
In this thesis,
while we proposed in Chapter~\ref{chapter:5} any-time algorithms solving the presented problem of stationary multi-players bandit, our solution for the problem of non-stationary MAB problem studied in Chapter~\ref{chapter:6} does rely on a prior knowledge of the horizon $T$.
It is an interesting direction of research to know what is the best approach to fix this weakness: work more and design algorithms that are inherently any-time, or use a generic technique to avoid depending on a prior knowledge of $T$, and automatically transform our non-anytime approach to make it anytime.

\paragraph{Solution to ``patch'' a non-anytime algorithm.}
%
A well-known technique to obtain an anytime algorithm from any non-anytime algorithm is the ``Doubling Trick'', as first introduced in \cite{CesaLugosi06} and used for instance in \cite{Auer10,AuerGajaneOrtner18}.
%
In the context of adversarial or stochastic multi-armed bandits,
the performance of an algorithm is measured by its regret,
and we study two families of sequences of growing horizons (geometric and exponential)
to generalize previously known results that certain doubling tricks can be used to conserve certain regret bounds.
In a broad setting, we prove that a geometric doubling trick can be used to conserve (minimax) bounds in $R_T = \cO(\sqrt{T})$ but \emph{cannot} conserve (distribution-dependent) bounds in $R_T = \cO(\log(T))$.
We give insights as to why exponential doubling tricks may be better, as they conserve bounds in $R_T = \cO(\log(T))$, and are close to conserving bounds in $R_T = \cO(\sqrt{T})$.
Interestingly, we prove that they conserve bounds of the mixed form $R_T = \cO(T^{\gamma} (\log(T))^{\delta})$, for $0<\gamma<1$ and $\delta>0$, and so an exponential doubling trick could be used to obtain an anytime version of the algorithm we propose for non-stationary bandits, \GLRklUCB{} in Chapter~\ref{chapter:6}.
However, our study was only focussing on stationary bandit, and it is left as a future work to explore the harder case of piece-wise stationary problems.

@@

To conclude this work, we would need to complete the study of the doubling tricks, and instead of focussing on two families (geometric and exponential), we need to completely characterize the doubling tricks that allow to preserve certain regret bounds.
Such doubling is given either by the function mapping the current time $t$ to the current estimate of the horizon $T(t)$, or the sequence $(T_i)_{i\in\N^*}$ of successive estimates of the horizons.
We are interested in pursuing this work, in the hope of finding an intermediate sequence, growing faster than a geometric but slower than an exponential doubling sequence, that can preserve both worlds, problem-dependent bounds in $\cO(\log(T))$ and problem-independent bounds in $\cO(\sqrt{T})$.
